---
title: "Visualize Data"
author: "Audrey Longan"
format: gfm
execute: 
  echo: true
  eval: true
---


<!-- If you get the error "Error in list2(na.rm = na.rm, ...) : object 'ffi_list2' not found" do the following in the Console run:  

    remove.packages("rlang")

Then Restart R to be safe. Then run:

    install.packages("rlang")

and again restart R to be safe. That should fix the problem (which is a package dependency issue).   -->



Try your code again
```{r}
#| label: setup
#| include: false

library(tidyverse)

```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: first-rows-mpg
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: mpg-scatterplot
#add code
ggplot(mpg) +
  geom_point(aes(x = displ, y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: mpg-boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: mpg-histogram
ggplot(mpg) +
  geom_histogram(aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: mpg-histogram-bins2

ggplot(mpg) +
  geom_histogram(aes(x = hwy), binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: mpg-scatterplot-experiment
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, 
                           y = hwy,
                           color = class,
                           shape = class,
                           alpha = class,
                           size = class)) +
  labs(x = "Engine Size Displacement",
       y = "Highway Mileage (mpg)",
       title = "The bigger the engine the less mileage on the highway") +
  theme_light()
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: facets
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl) #makes one row, 4 columns by cyl
q + facet_grid(drv ~ .) #makes 3 rows, one column by drv
q + facet_grid(drv ~ cyl) #makes 3 rows by drv, 4 columns by cyl
q + facet_wrap(~ class) #makes a graph for each value in the class
```

Facet grid makes a grid of graphs that relate to each other by specifying the variables that you want faceted, while facet wrap makes a grid of graphs based on a variable by stacking them until there is no more space, instead of making specific columns and rows.

## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
#| label: mpg-barplot-withclass

ggplot(mpg) +
  geom_bar(aes(x=class, fill = class)) +
  guides(fill = "none") +
  labs(x = "class of Vehicle",
       y = "Number of Vehicles in Sample") +
  theme_bw()
```

## Quiz

What will this code do?

```{r}
#| label: quiz
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth() 

ggsave("example.jpg")
```

This code will create a graphic with points and a best fit line of mpg data with displ on the x axis and hwy on the y axis. It adds two geometries to one plot.

***

# Take aways

You can use this starter code template to make thousands of graphs with **ggplot2**.

```{r}
#| label: template
#| eval: false
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```